\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, physics, bm}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\title{Derivation of Depolarizing Noise Covariances Using $R_{xy}(\phi)$ Rotations}
\author{}
\date{}

\begin{document}

\maketitle

\section*{Overview}
Depolarizing noise in a quantum system can be described using stochastic Lindblad operators that evolve unitarily under a rotation. We derive the variances and covariances of It\^o integrals associated with each Pauli component ($X$, $Y$, $Z$) when the Lindblad operators are rotated about an axis $R_{xy}(\phi)$ in the $xy$-plane.

\section*{Hamiltonian and Unitary Evolution}
We define the rotation axis in the $xy$-plane as:
\begin{equation}
R_{xy}(\phi) = \cos(\phi) X + \sin(\phi) Y.
\end{equation}

The Hamiltonian generating the rotation is:
\begin{equation}
H = \frac{\theta}{2} R_{xy}(\phi).
\end{equation}

This yields a unitary operator:
\begin{equation}
U(s) = \exp\left(-i s H\right) = \exp\left(-i s\theta R_{xy}(\phi)/2\right).
\end{equation}

We use the identity for exponentials of Pauli operators:
\begin{equation}
U(s) = \cos\left(\frac{s\theta}{2}\right) I - i \sin\left(\frac{s\theta}{2}\right) R_{xy}(\phi).
\end{equation}

\section*{Lindblad Evolution Model}
In the stochastic master equation framework, the noise is modeled by time-dependent Lindblad operators of the form:
\begin{equation}
L_{k,s} = U(s) L_k U^\dagger(s), \quad L_k \in \{I, X, Y, Z\}.
\end{equation}

To model noise in a particular observable , we track how each $L_k(s)$ projects onto $\sigma_k$. Define:
\begin{equation}
f_k^{(\sigma_k)}(s) = \frac{1}{2} \text{Tr}[L_k(s) X] = \frac{1}{2} \text{Tr}[U(s) \sigma_k U^\dagger(s) X].
\end{equation}
\[
L_{k,s} = f^{(I)} \cdot I + f^{(X)} \cdot X + + f^{(Y)} \cdot Y + f^{(Y)} \cdot Y
\]
since:
\[
\mathbb{E}[(\int_0^1 L_{k,s} dW_{k,s})^2] = \sum_k \int_0^1 f^{(\sigma_i)}_{k,s} ds \cdot \sigma_i
\]

These functions act as stochastic integrands for the It\^o process in the $X$-direction.

\section*{Computation of Basis Functions}
To compute the noise affecting the $X$ component, we extract:

\begin{align}
f_I = 
\\
f_1^{(X)}(s) &= \frac{1}{2} \text{Tr}[L_Z(s) X] = -\sin(\phi) \sin(s\theta), \\
f_2^{(X)}(s) &= \frac{1}{2} \text{Tr}[L_Y(s) X] = \sin(2\phi) \sin^2\left(\frac{s\theta}{2}\right), \\
f_3^{(X)}(s) &= \frac{1 - \frac{1}{2} \text{Tr}[L_X(s) X]}{2} = \sin^2\left(\frac{s\theta}{2}\right).
\end{align}

These functions describe the instantaneous coupling of rotated Lindblad operators to the $X$ axis.

\section*{It\^o Covariance Matrix}
We define the variances and covariances of the It\^o integrals by integrating products of these functions:
\begin{align}
V_k &= \int_0^1 f_k^2(s)\, ds, \\
\text{Cov}[f_i, f_j] &= \int_0^1 f_i(s) f_j(s)\, ds.
\end{align}

\subsection*{X - Component: $\phi = \pi/2$}
Choosing $\phi = \pi/2$ aligns the rotation with the $Y$-axis. The corresponding projections yield:
\begin{align*}
f_1^{(X)}(s) &= -\sin(s\theta), \\
f_2^{(X)}(s) &= 0, \\
f_3^{(X)}(s) &= \sin^2\left(\frac{s\theta}{2}\right).
\end{align*}

Resulting variances:
\begin{align*}
V_1^{(X)} &= \int_0^1 \sin^2(s\theta)\, ds = \frac{2\theta - \sin(2\theta)}{4\theta}, \\
V_2^{(X)} &= 0, \\
V_3^{(X)} &= \int_0^1 \sin^4\left(\frac{s\theta}{2}\right)\, ds = \frac{6\theta - 8\sin(\theta) + \sin(2\theta)}{16\theta}.
\end{align*}

And covariance:
\begin{equation*}
\text{Cov}[f_1, f_3] = \int_0^1 \sin(s\theta)\sin^2\left(\frac{s\theta}{2}\right)\, ds = \frac{\sin^4(\theta/2)}{\theta}.
\end{equation*}

\subsection*{Y - Component: $\phi = 0$}
Choosing $\phi = 0$ aligns the rotation with the $X$-axis. The corresponding projections yield:
\begin{align*}
f_1^{(Y)}(s) &= \sin(s\theta), \\
f_2^{(Y)}(s) &= 0, \\
f_3^{(Y)}(s) &= \sin^2\left(\frac{s\theta}{2}\right).
\end{align*}

Resulting variances:
\begin{align*}
V_1^{(Y)} &= \int_0^1 \sin^2(s\theta)\, ds = \frac{2\theta - \sin(2\theta)}{4\theta}, \\
V_2^{(Y)} &= 0, \\
V_3^{(Y)} &= \int_0^1 \sin^4\left(\frac{s\theta}{2}\right)\, ds = \frac{6\theta - 8\sin(\theta) + \sin(2\theta)}{16\theta}.
\end{align*}

And covariance:
\begin{equation*}
\text{Cov}[f_1, f_3] = \int_0^1 \sin(s\theta)\sin^2\left(\frac{s\theta}{2}\right)\, ds = \frac{\sin^4(\theta/2)}{\theta}.
\end{equation*}


\subsection*{Z - Component: ??}



\section*{Conclusion}
By rotating standard Pauli Lindblad operators using a unitary generated from $R_{xy}(\phi)$, and projecting onto a fixed observable, we derive the stochastic basis functions $f_k(s)$ that define the It\^o variance and covariance structure for depolarizing noise. This approach yields exact expressions for the X-component, and similar expressions can be derived for $Y$ and $Z$ using appropriately chosen $\phi$ values to rotate around orthogonal directions.

\end{document}
